\textbf{Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated}

### 2022-09-22 submission/manuscript.Rmd
updatess

<!-- stakes and Post-truth era -->
For the first time in human history, technology has enabled the creation of near-perfect simulations indistinguishable from reality. These artificial, yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access [@nightingale2022]. Such developments not only carries important consequences for the technological and entertainment sectors, but also for security and politics - for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020]. This issue is central to what has been coined the "post-truth era" [@lewandowsky2017beyond], in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.

@@

In the first part of the study, participants answered a series of personality questionnaires, including the *Mini-IPIP6* [24 items, @sibley2011] measuring 6 personality traits, the *SIAS-6* and the *SPS-6* [6 items each, @peters2012development] assessing social anxiety levels, the *FFNI-BF* [30 items, @jauk2022validation] measuring 9 facets of narcissism; the *R-GPTS* [18 items, @freeman2021revised] measuring 2 dimensions related to paranoid thinking; and the *IUS-12* [12 items, @carleton2007fearing] measuring intolerance to uncertainty. Finally, we devised 5 items pertaining to expectations about AI-generated images technology ("I think current Artificial Intelligence algorithms can generate very realistic images"). To lower their saliency and the possibility of it priming the subjects about the task, we mixed these items with 5 items from the general attitudes towards AI scale [*GAAIS*, @schepman2020initial]. This scale was presented after the social anxiety questionnaires, and 3 attention check questions were embedded in the surveys.

In the second part of this study, 109 photos of neutral-expression faces of real individuals from the validated American Multiracial Face Database (AMFD, [@chen2021broadening]) were presented to the participants for 50 0ms each, in a randomized order, following a fixation cross display (750 ms). After each stimulus presentation, ratings of *Trustworthiness* ("I find this person trustworthy") and *Familiarity* ("This person reminds me of someone I know") were collected using visual analog scales. Notably, as facial attractiveness is a multidimensional construct, encompassing evolutionary, sociocultural, biological as well as cognitive aspects [@rhodes2006evolutionary; @han2018beauty], we assessed attractiveness using 2 scales, measuring general *Attractiveness* ("I find this person attractive") and physical *Beauty* ("This face is good-looking").

In the last part of the study, participants were informed that about half of the face images previously seen were AI-generated (the instructions used a cover story mentioning that the research was aimed at validating a new face generation algorithm). The same set of stimuli was displayed again for 500 ms in a new randomized order. This time, after each display, participants were asked to express their belief regarding the nature of the stimulus using a visual analog scale (with *Fake* and *Real* as the two extremes). The study was implemented using *jsPsych* [@de2015jspsych], and the exact instructions are available in the experiment code.

@@

One hundred and three participants were recruited via *Prolific*, a crowd-sourcing platform recognized for providing high quality data [@peer2022]. The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood. Participants were incentivised with a reward of about \textsterling 7.5 for completing the study, which took about 45 minutes to finish. Demographic variables (age, gender, sexual orientation, education and ethnicity) were self-reported on a voluntary basis.

@@

The real-fake ratings (measured originally on a [-1, 1] analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous *belief* (real or fake, derived based on the sign of the rating) and the *confidence* (the rating's absolute value) associated with that belief. The former was analyzed using logistic mixed models (with the participants and images entered as random factors), which models probability of assigning a face to the real (>= 0) as opposed to fake (< 0). The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity) was modeled using beta regression models (suited for outcome variables expressed in percentages).

We started by investigating the effect of the procedure and instructions to check whether the stimuli (which were real pictures of faces) were indeed judged as fake in a sufficient proportion to warrant their analysis. Additionally, we assessed the effect of the re-exposure delay, i.e., the time between the first presentation of the image (corresponding to the face ratings) and the second presentation (for the real-fake rating).

The determinants of reality beliefs were modeled separately for attractiveness, beauty, trustworthiness, and familiarity, using second order raw polynomials coefficients to allow for possible quadratic relationships (**Figure 2**. Aside from attractiveness (conceptualized as a general construct), models for beauty, trustworthiness and familiarity were adjusted for the the two remaining variables *mutatis mutandis*. We took into account the gender of participants and stimuli by retaining the pictures that were aligned with the participants' sexual preference (e.g., female faces for homosexual females, male faces for heterosexual females, and both for bisexual participants), and modeling the interaction with the participants' gender. For the attractiveness and beauty models, we then added the interaction with the reported self-attractiveness (the average of the two questions pertaining to it) to investigate its potential modulatory effect. Finally, we investigated the inter-individual correlates of simulation monitoring with similar models (but this time, for all items regardless of the participant's gender or sexual orientation) for each questionnaire, with all of the subscales as orthogonal predictors.

@@

Only one image file yielded a strong simulation monitoring bias (> 85\%), being classified as fake in 87.4\% of trials. This image was removed from further analysis, leaving 108 trials per participant. On average, across participants, 44\% of images (95\% CI [0.11, 0.64]) were judged as fake and 56\% of images (95\% CI [0.36, 0.89]) as real. An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 10.5% for the participants and 8.7% for the pictures.

@@

We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness ($R^2_{marginal}$ = 3.0%). However, a significant positive and linear relationship was found with the confidence in faces judged as real ($\beta_{poly1} = 9.31$, $95\% CI = [3.45, 15.17]$, $z = -3.11$, $p = .002$), and a quadratic relationship for faces judged as fake ($\beta_{poly1} = -12.67$, $95\% CI = [-19.87, -5.47]$, $z = -3.45$, $p < .001$; $\beta_{poly2} = 8.14$, $95\% CI = [0.01, 16.28]$, $z = 1.96$, $p = .05$), for males only, suggesting that faces are judged as real with more confidence when they are familiar, and judged as fake with less confidence when they are of not familiar or highly familiar.

@@

The models including the personality traits suggested that *Honesty-Humility* had a significant negative relationship predominantly with the confidence associated with faces judged as real ($\beta_{real} = -1.69$, $95\% CI = [-2.74, -0.63]$, $z = -3.14$, $p < .01$; $\beta_{fake} = -1.02$, $95\% CI = [-2.07, 0.03]$, $z = -1.90$, $p = 0.058$). Narcissism shared significant links through various dimensions, such as positive relationship between the confidence for both real and fake judgments and *Acclaim Seeking* ($\beta_{real} = 2.08$, $95\% CI = [0.79, 3.37]$, $z = 3.16$, $p < .01$; $\beta_{fake} = 1.60$, $95\% CI = [0.30, 2.90]$, $z = 2.42$, $p < .05$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.38$, $95\% CI = [-2.50, -0.27]$, $z = -2.43$, $p < .05$; $\beta_{fake} = -1.23$, $95\% CI = [-2.35, -0.11]$, $z = -2.15$, $p < .05$) and *Thrill Seeking* ($\beta_{real} = -0.93$, $95\% CI = [-1.75, -0.10]$, $z = -2.20$, $p < .05$; $\beta_{fake} = -1.03$, $95\% CI = [-1.87, -0.20]$, $z = -2.44$, $p < .05$). Finally, the social phobia dimension was significantly associated with a decreased probability of judging faces as fake ($\beta = -0.97$, $95\% CI = [-1.86, -0.08]$, $z = -2.14$, $p < .05$), but no effect on the confidence judgments was found. No significant relationships was found for intolerance to uncertainty or paranoid beliefs.

@@

<!-- Attractiveness: females -->
Although attractiveness did not seem to be the primary drive underlying simulation monitoring of face images, we do nonetheless report significant associations, with a different pattern observed depending on the participant's gender. The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real. The fact that this effect did not reach significance for beauty underlines that attractiveness judgments, and its role in simulation monitoring, are a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women **[REF?]**.

<!-- Attractiveness: males -->
Indeed, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring, that we could interpret under an evolutionary lens. Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial]. However, while it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering them significantly more salient than unattractive faces, in turn distorting the relationship with simulation monitoring. However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers [in particular, heart rate deceleration, @goldstein2002influence].

@@

<!-- trustworthiness -->
Our results suggested that trustworthiness ratings linearly increased beliefs in realness, for females only. Given the evidence suggesting that faces presented as real were rated as more trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such link to be present for both genders. One of the contributing mechanism to this dimorphism could have been the increased risk-taking aversion reported in females [explained evolutionarily as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival]. However, if that was the case, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real. As such, further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.

<!-- familiarity -->
Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions. However, the distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar. Future studies could re-examine this aspect by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before the simulation monitoring judgments.

<!-- inter-indiv correlates -->
Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with higher scores of honesty-humility, a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest], displayed a lower confidence in their simulation monitoring judgments. Given the negative correlation between honesty-humility and narcissism [@hodson2018dark], we put this result in perspective with the positive link observed with narcissistic acclaim seeking, confirming evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making [@campbell2004narcissism; @chatterjee2017master; @brunell2017narcissism; @o2021grandiose]. However, an inverse effect was found for other facets of narcissism, such as authoritativeness and thrill seeking. We interpret these effects as related to a higher response assertiveness and, for thrill seeking, tolerance of cognitive uncertainty (note that the tolerance to uncertainty scale, which mostly measures the anxiety associated with uncertain events, did not show any link). Taken together, these results suggest that participants with low humility, high recognition desires, and high excitement-seeking traits are more confident in their judgment regarding the real or fake nature of ambiguous stimuli. Participants with opposite traits might perceive a higher risk in the decision process and its potential consequences (e.g., being seen as bad at the task at hand), resulting in more conservative confidence ratings.

<!-- AI attitudes -->
Despite the ubiquity of AI, the literature pertaining on the influence of people's AI attitudes on simulation monitoring is scarce. Contrary to our expectations, we did not find evidence for the role of participants' expectations regarding the capabilities of AI technology (in terms of the realism of its productions). Instead, we found that one's enthusiasm about AI technology was related to an increased confidence in simulation monitoring ratings. It is possible that participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities [@said2022artificial], hence permitting themselves to be more confident in their simulation monitoring decisions. This result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications [@@said2022artificial].

<!-- Social phobia -->
However, it is to important note that all of the aforementioned dispositional traits did only influence the confidence judgments, but not the simulation monitoring bias *per se*. In fact, the only trait that modulated the tendency to rate an image as fake or real was the social phobia score, which low values were associated with an increased tendency of rating faces as real. **TODO: a bit of discussion, mostly on the fact taht the stimuli used were faces**.

>>>>

<!-- stakes and Post-truth era -->
For the first time in human history, technology has enabled the creation of near-perfect simulations indistinguishable from reality. These artificial, yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access [@nightingale2022]. Such developments not only carry important consequences for the technological and entertainment sectors, but also for security and politics - for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020]. This issue is central to what has been coined the "post-truth era" [@lewandowsky2017beyond], in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.

@@

In the first part of the study, participants answered a series of personality questionnaires, including the *Mini-IPIP6* [24 items, @sibley2011] measuring 6 personality traits, the *SIAS-6* and the *SPS-6* [6 items each, @peters2012development] assessing social anxiety levels, the *FFNI-BF* [30 items, @jauk2022validation] measuring 9 facets of narcissism; the *R-GPTS* [18 items, @freeman2021revised] measuring 2 dimensions related to paranoid thinking; and the *IUS-12* [12 items, @carleton2007fearing] measuring intolerance to uncertainty. Self-rated attractiveness was also assessed using 2 items - one measuring general attractiveness ("How attractive would you say you are?", @marcinkowska2021self) and the other measuring physical attractiveness ("How would you rate your own physical attractiveness relative to the average", @spielmann2020predictive).  Finally, we devised 5 items pertaining to expectations about AI-generated image technology ("I think current Artificial Intelligence algorithms can generate very realistic images"). To lower their saliency and the possibility of it priming the subjects about the task, we mixed these items with 5 items from the general attitudes towards AI scale [*GAAIS*, @schepman2020initial]. This scale was presented after the social anxiety questionnaires. 3 attention check questions were also embedded in the surveys.

In the second part of this study, 109 neutral-expression facial images of real individuals from the validated American Multiracial Face Database (AMFD, [@chen2021broadening]) were presented to the participants for 500ms each, in a randomized order, following a fixation cross display (750 ms). After each stimulus presentation, ratings of *Trustworthiness* ("I find this person trustworthy") and *Familiarity* ("This person reminds me of someone I know") were collected using visual analog scales. Notably, as facial attractiveness is a multidimensional construct, encompassing evolutionary, sociocultural, biological as well as cognitive aspects [@rhodes2006evolutionary; @han2018beauty], we assessed attractiveness using 2 visual analog scales, measuring general *Attractiveness* ("I find this person attractive") and physical *Beauty* ("This face is good-looking").

In the last part of the study, participants were informed that about half of the facial images previously seen were AI-generated (the instructions used a cover story which mentioned that the research was aimed at validating a new face generation algorithm). The same set of stimuli was displayed again for 500 ms in a new randomized order. This time, after each display, participants were asked to express their belief regarding the nature of the stimulus using a visual analog scale (with *Fake* and *Real* as the two extremes). The study was implemented using *jsPsych* [@de2015jspsych], and the exact instructions are available in the experiment code.

@@

103 participants were recruited via *Prolific*, a crowd-sourcing platform recognized for providing high quality data [@peer2022]. The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood. Participants were incentivised with a reward of about \textsterling 7.5 for completing the study, which took about 45 minutes to finish. Demographic variables (age, gender, sexual orientation, education and ethnicity) were self-reported on a voluntary basis.

@@

The real-fake ratings (measured originally on a [-1, 1] analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous *belief* (real or fake, derived based on the sign of the rating) and the *confidence* (the rating's absolute value) associated with that belief. The former was analyzed using logistic mixed models (with the participants and images entered as random factors), which modeled the probability of assigning a face to the real (>= 0) as opposed to fake (< 0). The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity) was modeled using beta regression models (suited for outcome variables expressed in percentages).

We started by investigating the effect of the procedure and instructions to check whether the stimuli (which were real images of faces) were indeed judged as fake in sufficient proportion to warrant their analysis. Additionally, we assessed the effect of the re-exposure delay, i.e., the time between the first presentation of the image (corresponding to the face ratings) and the second presentation (for the real-fake rating).

The determinants of reality beliefs were modeled separately for attractiveness, beauty, trustworthiness, and familiarity, using second order raw polynomials coefficients to allow for possible quadratic relationships (**Figure 2**). Aside from attractiveness (conceptualized as a general construct), models for beauty, trustworthiness and familiarity were adjusted for the the two remaining variables *mutatis mutandis*. We took into account the gender of participants and stimuli by retaining the images of faces that were aligned with the participants' sexual preference (e.g., female faces for homosexual females, male faces for heterosexual females, and both for bisexual participants), and modeling the interaction with the participants' gender. For the attractiveness and beauty models, we then added the interaction with the reported self-attractiveness (the average of the two questions pertaining to it) to investigate its potential modulatory effect. Finally, we investigated the inter-individual correlates of simulation monitoring with similar models (but this time, for all items regardless of the participant's gender or sexual orientation) for each questionnaire, with all of the subscales as orthogonal predictors.

@@

Only one image file yielded a strong simulation monitoring bias (> 85\%), being classified as fake in 87.4\% of trials. This image was removed from further analysis, leaving 108 trials per participant. On average, across participants, 44\% of images (95\% CI [0.11, 0.64]) were judged as fake and 56\% of images (95\% CI [0.36, 0.89]) as real. An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 10.5% for the participants and 8.7% for the images.

@@

We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness ($R^2_{marginal}$ = 3.0%). However, a significant positive and linear relationship was found with the confidence in faces judged as real ($\beta_{poly1} = 9.31$, $95\% CI = [3.45, 15.17]$, $z = -3.11$, $p = .002$), and a quadratic relationship for faces judged as fake ($\beta_{poly1} = -12.67$, $95\% CI = [-19.87, -5.47]$, $z = -3.45$, $p < .001$; $\beta_{poly2} = 8.14$, $95\% CI = [0.01, 16.28]$, $z = 1.96$, $p = .05$), for males only, suggesting that faces are judged as real with more confidence when they are familiar, and judged as fake with less confidence when they are not familiar or highly familiar.

@@

The models including the personality traits suggested that *Honesty-Humility* had a significant negative relationship predominantly with the confidence associated with faces judged as real ($\beta_{real} = -1.69$, $95\% CI = [-2.74, -0.63]$, $z = -3.14$, $p < .01$; $\beta_{fake} = -1.02$, $95\% CI = [-2.07, 0.03]$, $z = -1.90$, $p = 0.058$). Narcissism shared significant links through various dimensions, such as positive relationship between the confidence for both real and fake judgments and *Acclaim Seeking* ($\beta_{real} = 2.08$, $95\% CI = [0.79, 3.37]$, $z = 3.16$, $p < .01$; $\beta_{fake} = 1.60$, $95\% CI = [0.30, 2.90]$, $z = 2.42$, $p < .05$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.38$, $95\% CI = [-2.50, -0.27]$, $z = -2.43$, $p < .05$; $\beta_{fake} = -1.23$, $95\% CI = [-2.35, -0.11]$, $z = -2.15$, $p < .05$) and *Thrill Seeking* ($\beta_{real} = -0.93$, $95\% CI = [-1.75, -0.10]$, $z = -2.20$, $p < .05$; $\beta_{fake} = -1.03$, $95\% CI = [-1.87, -0.20]$, $z = -2.44$, $p < .05$). Finally, the social phobia dimension was significantly associated with a decreased probability of judging faces as fake ($\beta = -0.97$, $95\% CI = [-1.86, -0.08]$, $z = -2.14$, $p < .05$), but no effect on the confidence judgments was found. No significant relationships were found for intolerance to uncertainty or paranoid beliefs.

@@

<!-- Attractiveness: females -->
Although attractiveness did not seem to be the primary drive underlying simulation monitoring of face images, we do nonetheless report significant associations, with a different pattern observed depending on the participant's gender. The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real. The fact that this effect did not reach significance for beauty underlines that attractiveness judgment, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women [@buunk2002age; @qi2022gender].

<!-- Attractiveness: males -->
Indeed, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring, that we could interpret under an evolutionary lens. Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial; @buunk2002age]. However, while it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering them significantly more salient than unattractive faces and in turn distorted the relationship with simulation monitoring, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers [in particular, heart rate deceleration, @skora2022functional].

@@

<!-- trustworthiness -->
Our results suggested that trustworthiness ratings linearly increased beliefs in realness for females only. Given the evidence suggesting that faces presented as real were rated as more trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such a link to be present for both genders. One of the underlying mechanisms that possibly contributed to this dimorphism could have been the increased risk-taking aversion reported in females [explained evolutionarily as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival]. However, if that was the case, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real. As such, further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.

<!-- familiarity -->
Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions. However, it is to be noted that the distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar. Hence, future studies could re-examine this link (or lack thereof) by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items participants are subjected to before making simulation monitoring judgments.

<!-- inter-indiv correlates -->
Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with higher scores of honesty-humility, a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest], displayed a lower confidence in their simulation monitoring judgments. Given the negative correlation between honesty-humility and narcissism [@hodson2018dark], we put this result in perspective with the positive link observed with narcissistic acclaim seeking, confirming the evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making [@campbell2004narcissism; @chatterjee2017master; @brunell2017narcissism; @o2021grandiose]. However, an inverse effect was found for other facets of narcissism, such as authoritativeness and thrill seeking. We interpret the effects of the former as related to a higher response assertiveness and, for thrill-seeking, a tolerance of cognitive uncertainty (note that the intolerance to uncertainty scale, which largely measures the anxiety associated with uncertain events, did not show any link). Taken together, these results suggest that participants with low humility, high recognition desires, and high excitement-seeking traits are more confident in their judgment regarding the real or fake nature of ambiguous stimuli. Participants with opposite traits might perceive a higher risk in the decision process and its potential consequences (e.g., being seen as bad at the task at hand), resulting in more conservative confidence ratings.

<!-- AI attitudes -->
Despite the ubiquity of AI, the literature pertaining the influence of people's AI attitudes on simulation monitoring is scarce. Contrary to our expectations, we did not find evidence for the role of participants' expectations regarding the capabilities of AI technology (in terms of the realism of its productions). Instead, we found that one's enthusiasm about AI technology was related to an increased confidence in simulation monitoring ratings. It is possible that participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities [@said2022artificial], hence permitting themselves to be more confident in their simulation monitoring decisions. This result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications [@@said2022artificial].

<!-- Social phobia -->
However, it is important to note that all of the aforementioned dispositional traits did only influence the confidence judgments, but not the simulation monitoring bias *per se*. In fact, the only trait that modulated the tendency to rate an image as fake or real was the social phobia score, whereby low values were associated with an increased tendency of rating faces as real. This association could be put into perspective considering that the stimuli used were images of real faces, and social phobia is characterized as an abnormally extreme fear in social interaction contexts [@kolassa2006psychophysiological; @ran2017impact]. Specifically, previous studies have found social phobia to be related to neutral faces being perceived as more threatening [@yoon2008interpreting; @staugaard2010threatening; @peschard2017overestimation]. Whereas such reports indicate that individuals with greater social anxiety will perceive faces as more salient, hence suggesting that simulation monitoring decisions will be positively related to social phobia, we found opposing evidence that high social phobia scores were associated with increased ratings of faces being fake instead. This apparent contradiction could be explained through the lens of fictional reappraisal, an emotion regulation strategy in which people change their mental representations of the realness of a stimulus to manage their own emotional reactions [@sperduti2017distinctive; @sperduti2016paradox]. As the images of faces could have been perceived very negatively by individuals that are socially anxious, they may have spontaneously applied fictional reappraisal in processing the facial stimuli, thereby leading to an increased tendency to judge them as fake. Indeed, this is aligned with a previous study which reported that rates of belief in realness significantly decreased when pictures presented as real were emotional as compared to when they were neutral [@makowski2016phenomenal]. Given the implication of cognitive control abilities with fictional reappraisal [@hofmann2012executive; @schmeichel2010working], this hypothesis could hence be tested by assessing executive functions in relation to their simulation monitoring decisions in future studies.
